Lab2

### 2021-08-03 src/data/DataCleaning.Rmd

```{r clean dp03 data, echo=FALSE}
# filters by date/state
age <- dp05_age %>%
  rename(fips = GEO_ID,
         female = DP05_0003PE, 
         pct_lt5 = DP05_0005PE, 
         pct_5to9 = DP05_0006PE, 
         pct_10to14 = DP05_0007PE, 
         pct_15to19 = DP05_0008PE, 
         pct_20to24 = DP05_0009PE, 
         pct_25to34 = DP05_0010PE, 
         pct_35to44 = DP05_0011PE, 
         pct_45to54 = DP05_0012PE
) %>% rowwise() %>%
  mutate(
    fips = substring(fips, 10),
    female = as.double(female), 
    pct_lt5 = as.double(pct_lt5), 
    pct_5to9 = as.double(pct_5to9), 
    pct_10to14 = as.double(pct_10to14), 
    pct_15to19 = as.double(pct_15to19), 
    pct_20to24 = as.double(pct_20to24), 
    pct_25to34 = as.double(pct_25to34), 
    pct_35to44 = as.double(pct_35to44), 
    pct_45to54 = as.double(pct_45to54),
    pct_gt55 = 100 - sum(c(pct_lt5, pct_5to9, pct_10to14, pct_15to19, pct_20to24, pct_25to34, pct_35to44, pct_45to54)),
    pct_lt19 = sum(c(pct_lt5, pct_5to9, pct_10to14, pct_15to19)),
    pct_10to54 = 100 - pct_gt55 - pct_lt19
    ) %>%
  select(fips, pct_lt19, pct_10to14, pct_gt55)

>>>>

```{r clean dp03 data, echo=FALSE}
# filters by date/state
age <- dp05_age %>%
  rename(fips = GEO_ID,
         female = DP05_0003PE, 
         pct_lt5 = DP05_0005PE, 
         pct_5to9 = DP05_0006PE, 
         pct_10to14 = DP05_0007PE, 
         pct_15to19 = DP05_0008PE, 
         pct_20to24 = DP05_0009PE, 
         pct_25to34 = DP05_0010PE, 
         pct_35to44 = DP05_0011PE, 
         pct_45to54 = DP05_0012PE
) %>% rowwise() %>%
  mutate(
    fips = substring(fips, 10),
    female = as.double(female), 
    pct_lt5 = as.double(pct_lt5), 
    pct_5to9 = as.double(pct_5to9), 
    pct_10to14 = as.double(pct_10to14), 
    pct_15to19 = as.double(pct_15to19), 
    pct_20to24 = as.double(pct_20to24), 
    pct_25to34 = as.double(pct_25to34), 
    pct_35to44 = as.double(pct_35to44), 
    pct_45to54 = as.double(pct_45to54),
    pct_gt55 = 100 - sum(c(pct_lt5, pct_5to9, pct_10to14, pct_15to19, pct_20to24, pct_25to34, pct_35to44, pct_45to54)),
    pct_lt19 = sum(c(pct_lt5, pct_5to9, pct_10to14, pct_15to19)),
    pct_19to54 = 100 - pct_gt55 - pct_lt19
    ) %>%
  select(fips, pct_lt19, pct_19to54, pct_gt55)
